Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-13 paper.qmd
Updated Figure 4

two_curvy_proj_tsne_first_model1 <- plot_proj(
    proj_obj = proj_obj1, 
    point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
    line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
    plot_limits = c(-0.6, 0.6), 
    axis_text_size = 2, 
    is_category = FALSE) +
  interior_annotation(label = "b", position = sc_ltr_pos, cex = 1) +
  theme(aspect.ratio = 1,
        legend.position = "none")

@@

two_curvy_proj_tsne_all_model1 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(0.1, 0.5, clr_choice), # size, alpha, color
  line_param = c(0.5, 0.5, "black"), # linewidth, alpha
  plot_limits = c(-0.5, 0.5), 
  axis_text_size = 2, 
  is_category = FALSE) +
  interior_annotation(label = "c", position = sc_ltr_pos, cex = 1) +
  theme(aspect.ratio = 1) #+
  #geom_segment(
  #  data = model_df, 
  #  aes(
  #    x = proj1_from, 
  #    y = proj2_from, 
  #    xend = proj1_to, 
  #    yend = proj2_to), 
  #  color = "#000000")

>>>>

two_curvy_proj_tsne_first_model1 <- plot_proj(
    proj_obj = proj_obj1, 
    point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
    line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
    plot_limits = c(-0.6, 0.6), 
    axis_text_size = 2, 
    is_category = FALSE) +
  interior_annotation(label = "b", position = sc_ltr_pos, cex = 1.2) +
  theme(aspect.ratio = 1,
        legend.position = "none")

@@

two_curvy_proj_tsne_all_model1 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(0.1, 0.5, clr_choice), # size, alpha, color
  line_param = c(0.5, 0.5, "black"), # linewidth, alpha
  plot_limits = c(-0.5, 0.5), 
  axis_text_size = 2, 
  is_category = FALSE) +
  interior_annotation(label = "c", position = sc_ltr_pos, cex = 1.2) +
  theme(aspect.ratio = 1) #+
  #geom_segment(
  #  data = model_df, 
  #  aes(
  #    x = proj1_from, 
  #    y = proj2_from, 
  #    xend = proj1_to, 
  #    yend = proj2_to), 
  #  color = "#000000")
